Global SOC maps and emissions

### 2020-12-14 ResultNotebooks/results_SOCflows.Rmd
update fow fig

LivstCropLoss     <- CropFEED - ManureExcretedTot - LivstCropHANPP 
CropPRIMLoss      <- CropPRIM + ResPRIM + LivstCropHANPP - dimSums(grepSpaceTimeC(FAOmassbalance[,,c(kcr,kli,kres)][,,"other_util"]), dim=3) # only material use is not re-emitted

@@

write.magpie(TotalSOCBudget, paste0(outputdir,"TotalSOCBudget.cs3"))

>>>>

LivstCropLoss     <- CropFEED - ManureExcretedTot - LivstCropHANPP 
CropPRIMLoss      <- CropPRIM + ResPRIM + LivstCropHANPP # assume verything gets re-emitted at the end

@@

write.csv(as.data.frame(TotalSOCBudget), paste0(outputdir,"TotalSOCBudget.csv"))
